Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-01-22 paper.tex
Added maximum and minimum current density figures to CPE measurement

\section{Displacement Parameters}
The linear, or small-signal, part of an electrode-electrolyte interface is represented by a Constant Phase Element (CPE) or fractional capacitor. For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} Measurement of the CPE is made by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3. The numbering pattern used to identify each of the electrodes on the Octrode is shown in figure~\ref{fig:octrode}.
Measurements made using this configuration allow for the quantification of a single interface impedance in series with the resistance presented by the bulk solution.
Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results. Figure~\ref{fig:CPE_Phase} shows the phase response for the same measurements, again with the simulated response at each concentration. The simulated responses are generated using the optimised parameter values presented in Table~\ref{tab:CPEparams}. Those values were chosen as they give the closest match to the measured data.

@@

@@

page 2 Measurement of the CPE. What was the current density used in EIS measurements?
What is the effect of chosen current density on CPE impedance (Fig. 5)?
{\color{OliveGreen}
    Item 10\\
    {\color{Red} Estimate current density and investigate possible effects}
    No response yet.
}

>>>>

\section{Displacement Parameters}
The linear, or small-signal, part of an electrode-electrolyte interface is represented by a Constant Phase Element (CPE) or fractional capacitor. For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} Measurement of the CPE is made by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3. The numbering pattern used to identify each of the electrodes on the Octrode is shown in figure~\ref{fig:octrode}.
Measurements made using this configuration allow for the quantification of a single interface impedance in series with the resistance presented by the bulk solution. Current density during measurements peaked at $11.5\thinspace A/m^{2}$ at 10\thinspace kHz in 1.0X PBS and fell as low as $0.0141\thinspace A/m^{2}$ at 50\thinspace mHz in 0.025X PBS. 
Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results. Figure~\ref{fig:CPE_Phase} shows the phase response for the same measurements, again with the simulated response at each concentration. The simulated responses are generated using the optimised parameter values presented in Table~\ref{tab:CPEparams}. Those values were chosen as they give the closest match to the measured data.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Check that these are in the right order!!!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibitem{Weiland2000}
Weiland~James~D. and Anderson~David~J.,
``Chronic Neural Stimulation with Thin-Film, Iridium Oxide Electrodes'',
{\em IEEE Transactions on Biomedical Circuits and Systems},
vol.~47 no.~7, July 2000, pp911--918

@@

page 2 Measurement of the CPE. What was the current density used in EIS measurements?
What is the effect of chosen current density on CPE impedance (Fig. 5)?
{\color{OliveGreen}
    Item 10\\
    {\color{Red} Estimate current density and investigate possible effects}
    Maximum and minimum current density figures added. No comment on effect formed yet. No response yet.
}
